Proof by reflection for equalities in algebraic structures

### 2014-06-25 newPaper/paper.tex
paper continued... I AM LATE ARRRGH

We will have one datatype for reflected terms in each algebraic structure.

\begin{code}[caption=Reflected terms in a Magma, captionpos=b, label=lst1:haskell2]  
data ExprMa : Magma c -> (Vect n c) -> c -> Type where
    ConstMa : (p : Magma c) -> (g:Vect n c) -> (c1:c)  -> ExprMa p g c1 
    PlusMa : {p : Magma c} -> {g:Vect n c}  -> {c1:c} -> {c2:c} -> ExprMa p g c1 -> ExprMa p g c2 -> ExprMa p g (Plus c1 c2) 
    VarMa : (p:Magma c) -> {g:Vect n c} -> {c1:c} -> VariableA (magma_eq_as_elem_of_set p) g c1 -> ExprMa p g c1
\end{code}

>>>>

We will have one datatype for reflected terms in each algebraic structure. \\
Blablabla

\begin{code}[caption=Reflected terms in a Magma, captionpos=b, label=lst1:haskell2]  
data ExprMa : Magma c -> (Vect n c) -> c -> 
              Type where
    ConstMa : (p : Magma c) -> (g:Vect n c) 
               -> (c1:c)  -> ExprMa p g c1 
    PlusMa : {p : Magma c} -> {g:Vect n c}
               -> {c1:c} -> {c2:c} 
               -> ExprMa p g c1 -> ExprMa p g c2 
               -> ExprMa p g (Plus c1 c2) 
    VarMa : (p:Magma c) -> {g:Vect n c}
               -> {c1:c} 
               -> VariableA (get_eq_magma p) g c1
               -> ExprMa p g c1
\end{code}

For the moment, the definition of $Variable$ is just the following:

\begin{code}[caption=Reflected variables, captionpos=b, label=lst1:haskell2]  
data Variable : {c:Type} -> {n:Nat} -> 
         (c_equal : (c1:c) -> (c2:c) -> Maybe(c1=c2)) 
      -> (Vect n c) -> c -> Type where
    RealVariable :
             (c_equal:(c1:c)->(c2:c)->Maybe(c1=c2))
             -> (g:Vect n c) -> (i:Fin n) 
             -> Variable c_equal g (index_reverse i g) 
\end{code}

And $get\_eq\_magma$ is just a function which returns the equality test of the $Set$ level.
